Network graphs in ggraph

### 2016-05-27 104-network-graphs-in-ggraph.Rmd
Updates to network graph

```{r}
ggraph(codes_g, "igraph", algorithm = "fr") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 6) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name)) +
  labs(title = "Code to code borrowings") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```

@@

```{r}
ggraph(states_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(size = 6, alpha = 0.75, aes(color = region)) +
  geom_node_text(aes(label = name)) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
  ggforce::theme_no_axes() +
  labs(title = "State to state borrowings") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```

>>>>

```{r fig.width=12, fig.height=12}
ggraph(codes_g, "igraph", algorithm = "fr") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 6) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name)) +
  labs(title = "Code to code borrowings") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```

@@

```{r}
ggraph(states_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(size = 6, alpha = 0.75, aes(color = region)) +
  geom_node_text(aes(label = name)) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
  scale_color_manual(values = c("South" = "steelblue1",
                                "West" = "coral2",
                                "Atlantic" = "darkgoldenrod2",
                                "New England" = "mediumorchid2",
                                "Midwest" = "palegreen2",
                                "New York" = "peru")) + 
  ggforce::theme_no_axes() +
  labs(title = "State to state borrowings") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```
